\large \textbf Autonomous Quadrotor Landing on a Moving Platform in Outdoor Environments

### 2017-02-07 docs/paper/paper.tex
Update paper

% PROBLEM FORMULATION
\section{Problem Formulation}

@@

\subsection{Illumination Invariant AprilTag}
A common issue in computer vision is illumination changes in the
environment which in turn interferes with the performance of detection
algorithms. From our experience the standard black and white AprilTag
fails to be detected if a shadow is casted partially or fully upon the tag
features, this is because the AprilTag detection relies heavily on the
edges and lines of the tag to be able to estimate the 6dof pose.

Reliable image processing regardless of the time of day is vital to the
success of target detection. Using methods described in~\cite{Maddern14}
we have idenitified the best colours for an illumination invariant
AprilTag to be blue and green (see
Fig~\ref{apriltag_illumination_invariant}), additionally

@@

\subsection{Measurement Model}

\begin{equation}
  h(t) = \begin{bmatrix} p_{1 \times 3} & {0}_{1 \times 4} \end{bmatrix}
\end{equation}

% GIMBAL TRANSFORMS
\section{Gimbal Transforms}

Transform detected target from image frame to gimbal joint frame

@@

Gimbal joint frame to body planar frame

@@

Body planar frame to inertial frame

@@

@@

@@

\begin{equation}
  \begin{split}
    \textbf{x}_{0} = \begin{bmatrix}
        x_{0} & \dot{x_{d}} & z_{d} & \dot{z_{d}}
    \end{bmatrix}^{T} \\
    \textbf{x}_{d} = \begin{bmatrix}
        x_{d} & \dot{x_{d}} & z_{d} & \dot{z_{d}}
    \end{bmatrix}^{T}
  \end{split}
\end{equation}

@@

@@

@@

% QUADROTOR CONTROL
\section{Quadrotor Control}
For target tracking a Proportional-Integral-Derivative (PID) controller
was implemented. The estimated target position in inertial frame is
converted to body frame and used as control errors to the tracker control

>>>>

% SYSTEM OVERVIEW
\section{System Overview}
In this section we describe the setup of our problem, from the quadrotor,
ground landing target to coordinate systems used to represent positions in
body and inertial frames.

For the autonomous landing problem we assume that the quadrotor has direct line
of sight to the landing target and that the AprilTag is detectable. The target
position and velocity estimation is performed on-board the quadrotor, and
using the estimations of the target the quadrotor tracks and lands onto the
target.

\begin{itemize}
  \item{$I$\@: Inertial Frame}
  \item{$C$\@: Camera Frame}
  \item{$G$\@: Gimbal Frame}
  \item{$B$\@: Quadrotor Body Frame}
  \item{$BP$\@: Quadrotor Body Planar Frame}
\end{itemize}

We describe five different main coordinate frames used throughout this
paper, in general we have followed the ROS coordinate frame conventions
where the inertial frame $I$ is in ENU coordinate frame, the camera frame
$C$ is in EDN coordinate frame, gimbal frame $G$, quadrotor body frame $B$ and
quadrotor body planar frame $BP$ uses NWU coordinate frame. The quadrotor body
planar frame $BP$ is defined as the body centered and inertial horizon $x$-$y$
aligned frame, to reiterate the body planar frame $BP$ ignores the roll and
pitch (but not yaw) normally considered in a body frame $B$.

@@

\subsection{Illumination Invariant AprilTag}
A common issue in computer vision is illumination changes in the
environment which in turn interferes with the performance of detection
algorithms. From our experience the standard black and white AprilTag
fails to be detected if a shadow is casted partially or fully upon the tag
features, this is because the AprilTag detection relies heavily on the
edges and lines of the tag to be able to estimate the 6 dof pose.
Depending on the time of day or weather conditions, this can have
a significant impact as the quadrotor approaches the target, as its own
shadow over the AprilTag can render the tag undetectable.

Reliable image processing is therefore paramount to the success of target
detection, using methods described in~\cite{Maddern14} we have idenitified
the best colours for an illumination invariant AprilTag to be blue and
green (see Fig~\ref{apriltag_illumination_invariant}), additionally

@@

\subsection{Measurement Model}
The measurement inputted into the estimator is the target position ($x, y,
z$) in the inertial frame, the target position has been transformed from
the camera frame through to the gimbal frame to the inertial frame. Care
was taken to ensure that the IMU measurements were synchronized with image
of the AprilTag at the time it was captured.

To obtain the target position in the inertial frame, the detected target
position is first transformed from image frame to gimbal joint frame as
follows:

@@

Then from gimbal joint frame to body planar frame:

@@

Finally from body planar frame to inertial frame:

@@

This final target position in the inertial frame is then passed onto the
estimator. The measurement model $h(t)$ and the linearized measurement
model $H(t)$ at time $t$ is then simply

\begin{equation}
    h(t) = \begin{bmatrix} x, y, z \end{bmatrix}^{T}
\end{equation}

\begin{equation}
    H(t) = \begin{bmatrix} I_{3 \times 3} \end{bmatrix}^{T}
\end{equation}

The Extended Kalman Filter updates the process model at 200 Hz, while the
measurement is updated upon when the AprilTag is detected and transformed.
The output of the estimator is in turn used for tracking and landing.

@@

\subsection{2D Quadrotor Model}
The model used for trajectory planning is a two dimensional three degrees
of freedom (DOF) quadrotor in the $x$-$z$ plane. By using this model we
assume there will be small changes in the $x$-$y$ plane where the
controllers can correct without planning.

The 2D quadrotor state $\textbf{x}$ includes both position and velocity in the
$x$ and $z$ direction. Where $x_{0}$ and $x_{d}$ are the initial and final
states of the quadrotor. The inputs to the quadrotor model are the
acceleration $a_{z}$ in the $z$ direction in body frame, and pitch angle
$\theta$ in inertial frame.

@@

\begin{equation}
  \begin{split}
    \textbf{x}_{0} = \begin{bmatrix}
        x_{0} & \dot{x_{0}} & z_{0} & \dot{z_{0}}
    \end{bmatrix}^{T} \\
    \textbf{x}_{d} = \begin{bmatrix}
        x_{d} & \dot{x_{d}} & z_{d} & \dot{z_{d}}
    \end{bmatrix}^{T}
  \end{split}
\end{equation}

@@

The dynamics are thus given as:

@@

Where $g$ is the gravitational constant.

\subsection{Trajectory Problem Formulation}
The objective of the trajectory is to achieve landing of the quadrotor
onto a non-stationary target at $\textbf{x}_{d}$, further the trajectory
has to satisfy a number of desirable soft constraints, which are minimal
deviation from desired path $p_{\text{diff}}$, minimal total input
$u_{\text{total}}$ and minimal input control difference between time steps
$u_{\text{diff}}$.

The desired path $\textbf{p}_{\text{desired}}$ vector is a straight-line
from initial position $x_{0}$ to final position $x_{d}$.

\begin{equation}
    p_{\text{diff}} = || \textbf{x} - \textbf{p}_{\text{desired}} ||^{2}
\end{equation}

\begin{equation}
    u_{\text{total}} = || \textbf{u} ||^{2}
\end{equation}

\begin{equation}
    u_{\text{diff}} = \sum_{i = 0}^{t_{f} - 1}
        \left\Vert
            \textbf{u}(i + 1) - \textbf{u}(i)
        \right\Vert^{2}
\end{equation}

\begin{equation}
    J(\textbf{x}, \textbf{u}) =
        w_{1} \cdot p_{\text{diff}}
        + w_{2} \cdot u_{\text{total}}
        + w_{3} \cdot u_{\text{diff}}
\end{equation}

\begin{equation}
  C_{\text{eq}} = \sum_{i = 0}^{t_{f} - 1}
    \textbf{x}(i + 1) - f(\textbf{x}(i), \textbf{u}(i))
\end{equation}

@@

% QUADROTOR CONTROL
\section{Quadrotor Control}

\subsection{Tracking Controller}
For target tracking two PID controllers were implemented, first a position
based controller that corrects positional errors of the quadrotor relative
to the target. Second, a velocity based controller that uses estimated
target velocity as a feed-forward signal to match the target's velocity.
The two controllers are combined together to form the tracking controller.

\begin{equation}
   \theta = k_{p} e + k_{i} \sum_{i = 0}^{t} e_{i} dt + k_{d} \dot{e}
\end{equation}

\begin{figure}
\label{fig:tracking_controller}
  \includegraphics[width=\linewidth]{images/tracking_controller}
  \caption{Tracking Controller}
\end{figure}

\subsection{Landing Controller}
During landing the controller will be switched from tracking to landing,
the controller contains two PID controllers the first controller is
a position based control to correct positional errors of the quadrotor
relative to the target in the body frame.
